Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.3.0, thanks help from grammarly.

  Image classification and categorization are essential for the capability of telling the difference between images for a machine.
  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved an accuracy of $97.72\%~99.60\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%~98.95\%$ on the CIFAR-100 image set.

@@

%-------------------------------------------------------------------------
\section{Per-pixel Encoder}

For the per-pixel image classification approach, for every RGB channel of pixel in a image,
each pixel had its pixel-channel code, ranges from $0x00$ to $0xff$ for different colors.
Thus, taking these pixels in a image is identical to ASCII characters in a document.
Generality speaking, the performance of the pre-trained language models achieved in document classification task, can be transferred to image classification naturally.

@@

\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial dataset, which have 2 and 4 main domains.
The $Case-2$ dataset annotated civil and criminal cases, and the $Case-4$ dataset annotated by civil, criminal, intellectual property, and administrative cases.
The $Case-2$ dataset has $19508$ training documents and $2000$ test documents, and the $Case-4$ dataset has $34789$ training documents and $2013$ test documents.

@@

\section{Image Classification Model}

@@

We design a simple classification models without too many layers, as Figure-1 shows.
And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
The model architecture has seven functional layers:
\begin{itemize}
\item {\bf Input layer}
\item {\bf Concat layer}
\item {\bf Trim layer}
\item {\bf Encoder layer}
\item {\bf Embedding layer}
\item {\bf Feature Extraction layer}
\item {\bf Output layer}
\end{itemize}

@@

\section{Image Classification Model}

\subsection{Experiments and Results}

Use the proposed model, and we tried different pre-trained language models to see the impact on classification accuracy.
From the table-2, from line 2 and line 4, for the same size of dataset with larger classes, it need more epochs and training time for the classification model.
From line 2 and line 3, for the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
however, its training cost grows for the larger language model.
From line 3 and line 5, for the same fine-tuned language model, classes number has some impact on the accuracy,
the less classes the dataset has, the more accuracy the model can achieve.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 1	&	84.89\% \\
RBTL3  & CIFAR-10 & 1	&	97.72\% \\
RoBERTa-wwm-ext-large  & CIFAR-10 & 6	&	99.60\% \\
RBTL3  & CIFAR-100 & 6  & 	98.27\% \\
RoBERTa-wwm-ext-large & CIFAR-100 & 16 &	98.95\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.}
\end{table}

@@

 Compare to iGPT-L's accuracy of 96.3\% on the unaugmented CIFAR-10 dataset and 82.8\% on the CIFAR-100 dataset, our models has preferable better results.
The reason that the model's outstanding performance lie in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use extra language corpus of
$5.4$ billions of tokens of wiki data and other resources.
The transformers in the pre-trained language models use multiple layers for representing images, and maybe used in other Computer Vision task, \eg object detection, gesture prediction.

@@

This paper proposed a novel idea by using pre-trained language models for images representation, and take image classification as an exmaple for its performance.
Tests showed that the proposed model outperforms the iGPT-L model without augmentment on the image dataset,
the model achieved accuracy of $97.72\%~99.60\%$ on the CIFAR-10 image set,
and accuracy of $98.27\%~98.95\%$ on the CIFAR-100 image set.

>>>>

  Image classification and categorization are essential for the capability of telling the difference between images for a machine.
  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved an accuracy of $97.72\%\sim99.60\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.

@@

%-------------------------------------------------------------------------
\subsection{Approach}

My approach consists of a pre-training state followed by a fine-tuning stage.
In pre-training, I use BERT objectives and the sequence Transformer architecture to predict language tokens.

\par Given an unlabeled dataset $\Bbb X$, the BERT objective samples a sub-sequence $\Bbb S \in \{C\}$,
$C$ represents all possible tokens, and such that for each index $i \in \Bbb S$,
there is independent probability $15\%$ of appearing in $\Bbb S$,
name the token $M$ as the BERT mask.
Train the language model by minimizing the BERT objective of the "masked" elements $x_M$
conditioned on the "unmasked" ones $x_{\left[1,n\right]\backslash M}$.
\[
  \lambda = \mathop{\Bbb E}\limits_{x\sim\Bbb X} \mathop{\Bbb E}\limits_{M} \sum_{i\in S}{\bigl[-\log{p(x_i\mid x_{\left[1,n \right]\backslash M})\bigr]}}
\]

\par The transformer decoder takes the image pixels and meta characters sequence $x_1,\cdots,x_n$ and produces a $d$-dimensional
embedding for each position.
Then I use a fully connected layer as a non-linear function from embeddings to image class.
The dropout layer and the Softmax layer are used for better transfer performance between the training and the test dataset.

\subsection{Per-pixel Encoder}

For the per-pixel image classification approach, for every RGB channel of pixel in a image,
each pixel had its pixel-channel code, ranges from 0x00 to 0xff for different colors.
Thus, taking these pixels in a image is identical to ASCII characters in a document.
Generality speaking, the performance of the pre-trained language models achieved in document classification task, can be transferred to image classification naturally.

@@

\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial dataset, which have 2 and 4 classes.
The \textit{Case-2} dataset annotated civil and criminal cases, and the \textit{Case-4} dataset annotated by civil, criminal, intellectual property, and administrative cases.
The \textit{Case-2} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Case-4} dataset has $34789$ training documents and $2013$ test documents.

@@

\subsection{Image Classification Model}

@@

I design a simple classification models without too many layers, as Figure-1 shows.
And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
The model architecture has seven functional layers:
\begin{itemize}
\item {\bf Input layer}
\item {\bf Concat layer}
\item {\bf Trim layer}
\item {\bf Encoder layer}
\item {\bf Embedding layer}
\item {\bf Feature Extraction layer}
\item {\bf Output layer}
\end{itemize}

@@

\section{Experiments and Results}

\subsection{Training}

As Cui \etal~\cite{cui2019pre} reported that the training of RBT3 language model was based on Devlin \etal's
Chinese BERT-base language model and the training of RBTL3 and RoBERTa-large language model used randomized initialization.
Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
I use a batch size of 512 and train for $1\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
I set the learning rate to $10^{-4}$ and no warmed up or decay are used.
The dropout rate is $0.05$.

\par When fine-tuning, I check the accuracy of the trained model on the test set, and stopped training when it converges on $10^{-3}\sim10^{-4}$.

\subsection{Results}

Use the proposed model, and I tried different pre-trained language models to see the impact on classification accuracy.
From the table-2, for the same size of dataset with larger classes, it need more epochs and training time for the classification model.
For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
however, its training cost grows for the larger language model.
For the same fine-tuned language model, classes number has some impact on the accuracy,
the less classes the dataset has, the more accuracy the model can achieve.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 1	&	84.89\% \\
RBTL3  & CIFAR-10 & 1	&	97.72\% \\
RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
RBTL3  & CIFAR-100 & 6  & 	98.27\% \\
RoBERTa-large & CIFAR-100 & 16 &	98.95\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
RoBERTa-large is short for RoBERTa-wwm-ext-large.}
\end{table}

@@

 Compare to iGPT-L's accuracy of 96.3\% on the CIFAR-10 dataset without augmentation and 82.8\% on the CIFAR-100 dataset, our models has preferable better results.
The reason that the model's outstanding performance lie in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use extra language corpus of
$5.4$ billions of tokens of wiki data and other resources.
The transformers in the pre-trained language models use multiple layers for representing images, and maybe used in other Computer Vision task, \eg object detection, gesture prediction.

@@

This paper proposed a novel idea by using pre-trained language models for images representation, and take image classification as an example for its performance in Computer Vision tasks.
Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
the model achieved accuracy of $97.72\%\sim99.60\%$ on the CIFAR-10 image set,
and accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.
